Summary Tables

### 2020-02-12 summary_tables_outcomes.Rmd
Add anchors throughout the document

Click here: [change in yll](#change_in_yll_100k)

@@

@@

@@

@@

@@

@@

### Change in deaths due to injury

@@

### Change in deaths due to PA

@@

### Change in deaths due to AP

@@

### Change in deaths due to injury per 100,000

@@

### Change in deaths due to PA per 100,000
```{r}
pa_rates <- lapply(cities,function(x) rbind(pa_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000, Total=colSums(pa_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(pa_rates) <- cities
round_and_print(pa_rates,"Change in deaths due to PA per 100,000 in ")

@@

### Change in deaths due to AP per 100,000
```{r}

@@

### Change in YLLs due to injury

@@

### Change in YLLs due to PA
```{r}
pa_totals <- lapply(io,function(x){
  xx <- x$outcomes$pathway_hb$ylls
  xxx <- sapply(1:5,function(y){
    xxx <- rowSums(xx[,pa_cols[seq(y,length(pa_cols),by=5)]])
    sapply(sort(unique(xx$age_cat)),function(z)sum(xxx[xx$age_cat==z]))
  })
  colnames(xxx) <- scen_names
  xxx
  })
sum_and_round_and_print(pa_totals,"Change in YLLs due to PA in ")
```

### Change in YLLs due to AP
```{r}
ap_totals <- lapply(io,function(x){
  xx <- x$outcomes$pathway_hb$ylls
  xxx <- sapply(1:5,function(y){
    xxx <- rowSums(xx[,ap_cols[seq(y,length(ap_cols),by=5)]])
    sapply(sort(unique(xx$age_cat)),function(z)sum(xxx[xx$age_cat==z]))
  })
  colnames(xxx) <- scen_names
  xxx
  })
sum_and_round_and_print(ap_totals,"Change in YLLs due to AP in ")
```

@@

### Change in YLLs due to injury per 100,000

@@

### Change in YLLs due to PA per 100,000
```{r}
pa_rates <- lapply(cities,function(x) rbind(pa_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000, Total=colSums(pa_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(pa_rates) <- cities
round_and_print(pa_rates,"Change in YLLs due to PA per 100,000 in ")
```

### Change in YLLs due to injury AP 100,000
```{r}
ap_rates <- lapply(cities,function(x) rbind(ap_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000, Total=colSums(ap_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(ap_rates) <- cities
round_and_print(ap_rates,"Change in YLLs due to AP per 100,000 in ")
```

@@

### Change in deaths due to disease

@@

### Change in deaths due to disease per 100,000

@@

### Change in YLL due to disease

@@

## Change in YLL due to disease per 100,000 {#change_in_yll_100k}

>>>>

Click here: [change in yll](#change_yll_100k)

@@

### Change in deaths {#change_death}

@@

### Change in deaths per 100,000 {#change_death_100k}

@@

### Change in YLL {#change_YLL}

@@

### Change in YLLs per 100,000 {#change_YLL_age_100k}

@@

### Change in YLLs per 100,000 {#change_YLL_gender_age_100k}

@@

### Change in deaths due to injury {#change_death_injury}

@@

### Change in deaths due to PA {#change_death_PA}

@@

### Change in deaths due to AP {#change_death_AP}

@@

### Change in deaths due to injury per 100,000 {#change_death_injury_100k}

@@

### Change in deaths due to PA per 100,000 {#change_death_PA_100k}
```{r}
pa_rates <- lapply(cities,function(x) rbind(pa_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000, Total=colSums(pa_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(pa_rates) <- cities
round_and_print(pa_rates,"Change in deaths due to PA per 100,000 in ")

@@

### Change in deaths due to AP per 100,000 {#change_death_AP_100k}
```{r}

@@

### Change in YLLs due to injury {#change_yll_injury}

@@

### Change in YLLs due to PA {#change_yll_PA}
```{r}
pa_totals <- lapply(io,function(x){
  xx <- x$outcomes$pathway_hb$ylls
  xxx <- sapply(1:5,function(y){
    xxx <- rowSums(xx[,pa_cols[seq(y,length(pa_cols),by=5)]])
    sapply(sort(unique(xx$age_cat)),function(z)sum(xxx[xx$age_cat==z]))
  })
  colnames(xxx) <- scen_names
  xxx
  })
sum_and_round_and_print(pa_totals,"Change in YLLs due to PA in ")
```

### Change in YLLs due to AP {#change_yll_AP}
```{r}
ap_totals <- lapply(io,function(x){
  xx <- x$outcomes$pathway_hb$ylls
  xxx <- sapply(1:5,function(y){
    xxx <- rowSums(xx[,ap_cols[seq(y,length(ap_cols),by=5)]])
    sapply(sort(unique(xx$age_cat)),function(z)sum(xxx[xx$age_cat==z]))
  })
  colnames(xxx) <- scen_names
  xxx
  })
sum_and_round_and_print(ap_totals,"Change in YLLs due to AP in ")
```

@@

### Change in YLLs due to injury per 100,000 {#change_yll_injury_100k}

@@

### Change in YLLs due to PA per 100,000 {#change_yll_PA_100k}
```{r}
pa_rates <- lapply(cities,function(x) rbind(pa_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000, Total=colSums(pa_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(pa_rates) <- cities
round_and_print(pa_rates,"Change in YLLs due to PA per 100,000 in ")
```

### Change in YLLs due to injury AP 100,000 {#change_yll_AP_100k}
```{r}
ap_rates <- lapply(cities,function(x) rbind(ap_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000, Total=colSums(ap_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(ap_rates) <- cities
round_and_print(ap_rates,"Change in YLLs due to AP per 100,000 in ")
```

@@

### Change in deaths due to disease {#change_death_disease}

@@

### Change in deaths due to disease per 100,000 {#change_death_disease_100k}

@@

### Change in YLL due to disease {#change_yll_disease}

@@

## Change in YLL due to disease per 100,000 {#change_yll_disease_100k}
